Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Incluyendo lo de las trials para que quede más guay

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is a
dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
past behaviour and adapt the set of rules, or even inferring new ones,
in order to deal with potential security incidents that they might cause in the future. %FERGU: The user's "algo que falta"? o eso hace referencia a
        %su culpa? 
%"lo del usuario", literalmente. Pero mejorquitarlo - JJ
Then the system will react, in a non-intrusive way, to the potentially
dangerous sequence of actions (events) that the employees are conducting at
any time.

@@

MUSES will include some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
%cambiado
 such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.

But first, this work presents a brief overview of the main existing solutions in this environment. Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes.

>>>>

This work introduces a recently released system named
MUSES, from Multiplatform Usable Endpoint Security, which is a
dev\-ice\--in\-de\-pen\-dent end-to end user-centric tool, based on a
set of security rules defined as specifications of the Corporate
Security Policies. In addition, it has the ability of `learning' from the user's (the employees)
past behaviour and adapt the set of rules, or even inferring new ones,
in order to deal with potential security incidents that they might cause in the future. %FERGU: The user's "algo que falta"? o eso hace referencia a
        %su culpa? 
%"lo del usuario", literalmente. Pero mejorquitarlo - JJ
Then the system reacts, in a non-intrusive way, to the potentially
dangerous sequence of actions (events) that the employees are conducting at
any time. The MUSES system has been also tested in an actual company, with satisfactory results. The analysis of all data from these tests, and conclusions, are part of the future work.

@@

MUSES includes some important modules in it core, %FERGU: no habéis hablado de ese loop, decid mejor "core" (no lo cambio yo por si no tiene sentido)
%cambiado
 such as an Event Processor, which performs an event correlation task \cite{SurveyEventCorrelation_Tiffany02}, matching occurred events with rules to deal with them, and extracting threats that a Real-Time Risk and Trust Analysis Engine (RT2AE) \cite{RT2AE_SOTICS13} will process (along with other trust data and profiles), to select the best subset of policies.

But first, this work presents a brief overview of the main existing solutions in this environment. Then, a comparison between these tools and MUSES is also conducted, focusing on the advances beyond the state of the art that this novel system (being developed inside an European Project\footnote{\url{http://musesproject.eu/}} of the same name) includes .
